Supplementary Materials

### 2020-05-15 analysis/analysis.Rmd
Script to read in the subgroup relations from csv files.
Subgroup comparison tables.

It's clearly skewed, and negative display duration are impossible, so will fit a `glm` with `family = 'lognormal`.

@@

@@

```{r, fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}
prior_samples <- get_model_samples(m_prior)

@@

```{r fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals."}

@@

```{r}
my_models <- list()
comp_summary$eeg$index <- as.numeric(as.character(comp_summary$eeg$index))
comp_summary$threshold$index <- as.numeric(as.character(comp_summary$threshold$index))

@@

```{r compare_comparisons}
bind_rows(
  select(comp_summary$eeg, measurement, key, mean_value),
  select(comp_summary$threshold, measurement, key, mean_value)) %>%
  spread(measurement, mean_value) -> d

>>>>

It's clearly skewed, and negative display duration are impossible, so will fit a `glm` with `family = 'lognormal'`.

@@

## Subgroup Information

Import subgroup information and display a table of the relationships that we will be investigating.

```{r}
source("scripts/import_subgroup_comparisons.R")

glimpse(subgroups)
opts <- options(knitr.kable.NA = "")
knitr::kable(index_table, caption = "subgroup index")
```

```{r}
knitr::kable(normal_table, caption = "normal and non-normal subgroups")
```

@@

```{r, fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals.", cache=TRUE}
prior_samples <- get_model_samples(m_prior)

@@

```{r fig.cap="The density plot shows the distribution of the empirical data, while the blue line shows the 66% and 95% prediction intervals.", cache=TRUE}

@@

```{r, cache=TRUE}
my_models <- list()
comp_summary$eeg$index <- as.numeric(as.character(comp_summary$eeg$index))
comp_summary$threshold$index <- as.numeric(as.character(comp_summary$threshold$index))

@@

```{r compare_comparisons, cache=TRUE}
bind_rows(
  select(comp_summary$eeg, measurement, key, mean_value),
  select(comp_summary$threshold, measurement, key, mean_value)) %>%
  spread(measurement, mean_value) -> d
